### 2023-11-15 calculus.tex
tweak to conclusion

The supplemental material contains a complete formal sketch of both variants, and the untyped calculus and its related metatheory are mechanized in Agda.
Because of the untyped variant's simplicity, and because marking is defined separately, this mechanization can serve universally as a baseline for the correctness of approaches like the typed action calculus and perhaps other analyses that minimize re-marking.
We leave a complete assessment of this and other re-marking optimization approaches to future work, particular because Hazel is now moving toward the decoupled approach for future development.

>>>>

The supplemental material contains a complete formal sketch of both variants, and the untyped calculus and its related metatheory are mechanized in Agda.
Because of the untyped variant's simplicity, and because marking is defined separately, this mechanization can serve universally as a baseline for the correctness of approaches like the typed action calculus and perhaps other analyses that minimize re-marking.
We leave a complete assessment of this and other re-marking optimization approaches to future work, particularly because Hazel is now moving toward the decoupled approach for future development.
